Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-05-14 Multiresolution_framework/ltx/manuscript.tex
minor edit to covariance function

The stochastic IDE form of the Amari neural field formulation~\cite{Amari1977} is given by (see~\cite{Freestone2011} for a full derivation)
\begin{equation}\label{eq:DiscreteTimeModel}
	v_{t+1}\left(\mathbf{r}\right) = 
	\xi v_t\left(\mathbf{r}\right) + 
	T_s \int_\Omega { 
	    w\left(\mathbf{r},\mathbf{r'}\right)
	    f\left(v_t\left(\mathbf{r}'\right)\right) 
	\, \mathrm{d}\mathbf{r}'} 
	+ e_t\left(\mathbf{r}\right), 
\end{equation}
where in this first-order (in time) formulation of the model the membrane dynamics are included through the parameter $\xi=1-T_s/\tau$, $\tau$ is the membrane time constant and $T_s$ is the sampling time step. 
% The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$. The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977,Atay2005}. The components of the model are shown in Fig.~\ref{fig:Modelcomponents}
\begin{figure}[!t]
\centering
\includegraphics[scale=1]{./Graph/fig2.pdf}
\caption{ {\bf The IDE neural field model components}. (\textbf{A}) The Mexican hat (dotted line) and Wizard hat (solid line) connectivity kernels. (\textbf{B}) First order (dotted line) and second order (solid line) synaptic kernels. (\textbf{C}) A representative of the activation function.}
\label{fig:Modelcomponents}
\end{figure}
The term $e_t(\mathbf r)$ is a zero mean Gaussian disturbance, spatially colored but temporally white, with covariance function 
\begin{equation}
cov\left(e_{t}\left(\mathbf{r}\right),e_{t+t'}\left(\mathbf{r'}\right)\right)=\sigma_d\eta(\mathbf{r}-\mathbf{r'})\delta(t-t'),
\label{eq:FieldDisturbance}
\end{equation}
where \parham{$\eta(\mathbf{r}-\mathbf{r'})$ is a spatially homogeneous covariance function, $\sigma_d$ is disturbance variance} and $\delta(\cdot)$ is the Dirac-delta function. %$ = \varsigma v_t(\mathbf{r})$ \cite{VanRotterdam1982,Murphy2009}.

>>>>

The stochastic IDE form of the Amari neural field formulation~\cite{Amari1977} is given by (see~\cite{Freestone2011} for a full derivation)
\begin{equation}\label{eq:DiscreteTimeModel}
	v_{t+1}\left(\mathbf{r}\right) = 
	\xi v_t\left(\mathbf{r}\right) + 
	T_s \int_\Omega { 
	    w\left(\mathbf{r},\mathbf{r'}\right)
	    f\left(v_t\left(\mathbf{r}'\right)\right) 
	\, \mathrm{d}\mathbf{r}'} 
	+ e_t\left(\mathbf{r}\right), 
\end{equation}
where in this first-order (in time) formulation of the model the membrane dynamics are included through the parameter $\xi=1-T_s/\tau$, $\tau$ is the membrane time constant and $T_s$ is the sampling time step. 
% The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$. The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977,Atay2005}. The components of the model are shown in Fig.~\ref{fig:Modelcomponents}
\begin{figure}[!t]
\centering
\includegraphics[scale=1]{./Graph/fig2.pdf}
\caption{ {\bf The IDE neural field model components}. (\textbf{A}) The Mexican hat (dotted line) and Wizard hat (solid line) connectivity kernels. (\textbf{B}) First order (dotted line) and second order (solid line) synaptic kernels. (\textbf{C}) A representative of the activation function.}
\label{fig:Modelcomponents}
\end{figure}
The term $e_t(\mathbf r)$ is a zero mean Gaussian disturbance, spatially colored but temporally white, with covariance function 
\begin{equation}
cov\left(e_{t}\left(\mathbf{r}\right),e_{t+t'}\left(\mathbf{r'}\right)\right)=\sigma_d\eta(\mathbf{r}-\mathbf{r'})\delta(t-t'),
\label{eq:FieldDisturbance}
\end{equation}
where $\eta(\mathbf{r}-\mathbf{r'})$ is a spatially homogeneous covariance function, $\sigma_d$ is disturbance variance and $\delta(\cdot)$ is the Dirac-delta function. %$ = \varsigma v_t(\mathbf{r})$ \cite{VanRotterdam1982,Murphy2009}.
